Enter our title here

### 2017-07-27 manuscript.tex

\documentclass[]{tise_style}

@@

\author{Tessa Mcdonnel \\Statistics Department, California Polytechnic State University, San Luis Obispo}
%\author{Shannon Pileggi \\Statistics Department, California Polytechnic State University, San Luis Obispo}

@@

Check this out

>>>>

\documentclass{tise_style}
\usepackage{natbib}

@@

\author{Tessa Mcdonnel, Shannon Pileggi,  \\Statistics Department, California Polytechnic State University, San Luis Obispo}
%\author{Shannon Pileggi \\Statistics Department, California Polytechnic State University, San Luis Obispo}

\Abstract{ The text of your abstract.}

\Keywords{one, two, three}

@@

Check this out, Schubert said this \cite{Schubert13}.

Check this out, Campbell said this \cite{Campbell02} regularly, but cite this in parentheses \citep{Campbell02}.

Check this out, Chi said this \cite{Chi81}.

\bibliographystyle{ECA_jasa}
\bibliography{bibfile}
